Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-18 VMCAI-revised-version/final.tex
up

Hence we can see how adding transitions can 
turn a system that is not bounded resilient into one that is. 
\alain{à quoi sert cette remarque ?}

@@

@@

Continuous VASS \cite{DBLP:journals/tocl/BlondinFHH17} are a relaxation of classical discrete VASS in which transitions can be fired a fractional number of times, and consequently counters may contain a fractional number of tokens.

>>>>

% Hence we can see how adding transitions can 
% turn a system that is not bounded resilient into one that is. 
% \alain{à quoi sert cette remarque ?}

@@

 \begin{center}
	\begin{figure}
	\hspace{1.5cm}
\includegraphics[width=0.70\textwidth]{WSTS_taxonomy}
	\caption{A taxonomy of WSTS and variants.}
	\end{figure}
\end{center}

@@

Continuous VASS~\cite{DBLP:journals/tocl/BlondinFHH17}, or $\mathds{Q}^d$-VASS are a relaxation of classical discrete VASS in which transitions can be fired a fractional number of times, and consequently counters may contain a fractional number of tokens.
